Experience-Biased Symbolic Planning

### 2014-05-16 AAAI_AuthorKit/paper.tex
premidnight version with shorter intro

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
% AAAI format packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
% Additional packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
% END Additional packages
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Experience-Biased Symbolic Planning)
/Author (Aram Ebtekar, Mike Phillips, Sven Koenig, Maxim Likhachev)
/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Experience-Biased Symbolic Planning}
\author{Aram Ebtekar$^\dagger$ \and Mike Phillips$^\dagger$ \and Sven Koenig\thanks{University of Southern California, Los Angeles, CA 90089} \and Maxim Likhachev% <-this % stops a space
\thanks{Carnegie Mellon University, Pittsburgh, PA 15217}% <-this % stops a space
%
}
\maketitle
\begin{abstract}
\begin{quote}
Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
In this paper, we demonstrate how to augment symbolic planners with
experience graphs, using the HSP2 planner as a representative
example.
The resulting planners are able to trade off seamlessly
between plan quality and runtime and thus have advantages over past
plan-reuse techniques, such as planning by analogy.
We demonstrate experimentally that on many symbolic domains, our approach reduces the number of nodes that the HSP2 planner needs to consider by a factor of 2 or more while achieving about the same plan quality.
\end{quote}
\end{abstract}

\section{Introduction}
Planning entails finding action sequences that achieve a goal state.
In order to apply the language of graph theory, states are often thought of as nodes connected by action transitions.
A \textbf{plan} is a path from the start state to one of many goal states.
Despite the existence of classic polynomial-time search techniques, such as Dijkstra's algorithm, planning remains the crux of many difficult problems in AI.

@@

A recent approach builds \textbf{experience graphs} to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
The intuition is to remember previously generated paths so that, when a new start and goals are queried, a new path can be quickly generated by reusing subpaths from the E-graph.
A variant of weighted A* is employed which biases its focus toward the E-graph.
While this work demonstrates promising results in robot motion planning, E-graphs have never before been applied to symbolic domain representations such as the STRIPS language.

@@

Classically, case-based reasoning methods 
such as PRIAR~\cite{Kamb:92}, SPA~\cite{Hank:95}, MRL~\cite{Koeh:94}, and NoLimit~\cite{mljournal}
have been used recall 
previous plans that appear similar to the current problem and 
then adapt them to meet the new specifications.
Compared to these methods, our work reuses prior experience in
the context of modern weighted A* methods. We also provide
a bound on the suboptimality of the solution.

@@

OAKplan~\cite{Serina:2010:KFC:1860143.1860472} is a recent 
case-based reasoning method which converts 
planning instances to into a compact graph representation and 
then uses recent kernel methods for matching labeled graphs to select
a similar case to the problem at hand. The selected case is then 
adapted using LPG-ADAPT~\cite{Fox06planstability} LPG-ADAPT is a replanning method 
encourages \textit{plan stability}, which tries to make 
sure that the new plan is as similar to the previous plan as possible. 
The method also uses a modern heuristic search approach.

@@

\begin{defn} For $\epsilon\ge 1$, a heuristic $h$ is called \textbf{$\epsilon$-consistent} if $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$. $h$ is \textbf{consistent} if it is $1$-consistent. \end{defn}
\begin{thm} Given an $\epsilon$-consistent heuristic and expanding no node more than once, A* is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost \cite{LikGorThr-ara}. \end{thm}

@@

In a sense, a lot of work is wasted by estimating the cost to reach every atom, when we only require $g_S(G)$.
Later, we'll see how to make better use of this computation.

@@

E-graphs can improve total search time over a series of related queries on the same graph.
Formally, an E-graph is a subgraph of the state space.
We update it between queries, typically by adding the solution path from the previous search query.

Suppose we have a consistent heuristic $h(S,S')$ for the distance between arbitrary pairs of states.
That is, $h$ obeys the triangle inequality, is never dominated by an edge cost, and $h(S,S) = 0$ for all $S\in V$.
The E-graph heuristic $h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
To be precise, define

@@

Let $V^E$ be the union of the goal states and the E-graph's vertices.
In addition to following E-graph edges, we imagine it's possible to ``jump" from $S$ to $S'$ at cost $\epsilon^E h(S,S')$.
That is, let $c'(S,S') = \min\left(c^E(S,S'),~\epsilon^E h(S,S')\right)$

@@

Later, when generating $S \notin V^E$, we see that we have already precomputed costs of paths consisting of all but the first edge of $\pi$ according to the definition of $h^E(S)$. Thus, we derive the mathematically equivalent but much cheaper computation
\[h^E(S) = \min_{S'\in V^E} \left(\epsilon^E h(S,S') + h^E(S')\right)\]

\begin{thm}$h^E$ is $\epsilon^E$-consistent. \cite{phillips2012graphs}\end{thm}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Pentagon.png}
	\end{center}
	\caption{An example E-graph and corresponding heuristic computations.}
	\label{fig:example}
\end{figure}

@@

Now we combine the ideas from HSP2 and E-graphs to construct a domain-independent STRIPS planner which learns from experience. In STRIPS, a consistent heuristic $h(S,S')$ is given by the HSP-max estimate $g_S(S')$. We can compute $g_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of Algorithm \ref{alg:ComputeG}: each run provides us with $|V^E|$ of these results, yielding $(|V^E|)^2$ values in total.

@@

ComputeG($S$) implements the dynamic programming computation of $g_S$-values.
Each iteration of the outermost loop permanently fixes at least one $g_S(a)$ value, so it does at most $|A|+1$ iterations.
Multiplying nested loop iterations together and dropping cardinality signs for brevity, a conservative runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
Thus, each state generated costs $O(\mathbf{A^2O + V^EA})$ time.

@@

\begin{thm}
Provided there exists a path from initial state $I$ to a goal state $S\supseteq G$, the experience-biased HSP algorithm finds a path which is at most $\epsilon\epsilon^E$-suboptimal.
\end{thm}

@@

Finally, we remark that the Experience-Biased HSP algorithm is highly parallelizable, even if A* is retricted to expanding nodes sequentially. Recall that the sum, min and max functions are computable in logarithmic time using linearly many processors. Therefore, with minor adjustments, ComputeG($S$) has parallel depth $O(\mathbf{A\log A\log O})$. With $\mathbf{A\max(O,V^E)}$ processors, the total cost of generating a state is $O(\mathbf{(A\log O + \log V^E)\log A})$. Using even more processors, the cost of \textit{expanding} a state can be reduced to the same by generating its successors in parallel. If still more processors are available, some may dedicate to the task of preemptively computing $h^E$ for states that are likely to be generated in the future, e.g. near the A* frontier.

@@

\subsection{Experiment 1: Plan Completion}

In this experiment set, we solve several hundred problem instances across 18 domains from the test suite.
For each problem, we first plan without experiences, using the HSP-plus heuristic in an A* search with weight $\epsilon=5$.
This search acts as our scientific \textbf{control}.
If the control fails to find a solution within 5 seconds (on an Intel Core i7-2600), we discard the problem instance as being too difficult.
Otherwise, we record the plan cost and the number of states that were generated during the search.
Thus, we end up recording data for 321 problem instances.

For each of these, we run 3 additional searches using E-graphs, setting $\epsilon^E=5$ but reducing $\epsilon$ to 1, thus maintaining the same theoretical suboptimality bound.
Note that although $\epsilon = 1$, some inflation is implicit in the use of HSP-plus.
The latter may overestimate by a factor equal to the number of atoms in the goal in the worst case, but only if the atoms are highly coupled together.

The E-graph consists of 20\%, 50\% or 80\% of the edges selected at random from the control's solution path, over the 3 respective searches. For each of these, we again record the solution cost and number of nodes generated, and compare these figures against the control.
Define \textbf{speedup} as the ratio of the number of nodes generated in the control to the number generated in the E-graph search.
Likewise, define the \textbf{cost improvement} as the ratio of solution cost in the control to cost in the E-graph search.

Results are summarized in Table \ref{tab:percent}.
To estimate the typical range of speedups, we present the 25th and 75th percentile speedups among the instances of each domain.
The full data is plotted in Figured \ref{fig:s_20_0} to \ref{fig:s_80_0}.
We see that while performance in virtually unaffected in some domains, it's never substantially worsened, and in certain domains the experience helps greatly.
For example, results are highly encouraging in the Blocks domain.
Furthermore, Figure \ref{fig:c_50_0} shows that the solution quality remains competitive; indeed, we see that when E-graphs are employed, the path cost is slightly reduced on average.

@@

\subsection{Experiment 2: Plan Generalization}

The previous experimental setup tested our ability to interpolate and extrapolate from incomplete partial plans stored in memory; however, the experimental searches solved identically the same problems as the control used to generate the E-graph.
Now, we try changing the start and goal states by moving each of them a small distance within the state space. 
In this manner, we test how well E-graphs enable the planner to generalize to nearby but non-identical queries.

We narrow our focus to 13 domains, and take from each of them the same set of instances as in Experiment 1, yielding 218 problem instances in all.
This time, we save 100\% of the solution path found by the same control used in Experiment 1.
Then for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps of random walk along the graph, respectively.

Note that due to the unpredictable nature of random walks, the shortest-paths distances of the moved nodes from their initial positions is only bounded from above by the number of steps taken, and may vary widely.
In exactly one case out of the 3*218 = 654, this resulted in the goal already being achieved at the start state, with no nodes generated. In this case, we resolved the indeterminate form of the speedup $\frac 00$ to 1.

@@

Figures \ref{fig:s_20_0} to \ref{fig:s_100_50} display the individual speedups achieved over all of our experimental trials. We observe that cases in which E-graphs mislead the planner into generating more states are quite rare, so it seems experiences can only help. We set the bias parameters arbitrarily; tuning them by domain or problem size may well yield even better results.

@@

However, some additional work remains before state-of-the-art performance can be achieved.
Aside from engineering optimizations, parameter tuning, and integration with newer state-of-the-art heuristics, future work will need to consider more intelligent ways to generalize from the experiences encoded by E-graphs.
This presents a unique challenge in symbolic planning, as many distinct states which may even be a large distance apart in the state graph, may still be conceptually related.
Thus, a planner could potentially benefit by learning to transfer experiences between parts of the state space which are somehow related.
With such an approach, it would be essential to limit overgeneralization, so as not to waste time on a lot of false leads.

@@

We saw that by reusing pieces from past plans, E-graph-based planners can find solutions more quickly as they learn and acquire experiences. Many interesting directions remain for future investigation. It remains unclear how the bias parameters should be set. In addition, more advanced schemes will be needed to expand and prune E-graphs if they get large due to collecting a lot of solutions. Saving each computed plan seems like a good idea intuitively, but other possibilities may be worth investigating.

For STRIPS in particular, distinct states can actually be very similar, differing only by a few irrelevant atoms; hence, experiences should be transferable to inexact matches. However, it's crucial not to overgeneralize as that might simply lead to most of the graph being reweighted uniformly. The problem of generalization seem related to that of abstraction, or automatically extracting structural information from a symbolic domain or problem description.

E-Graphs should be thought of not so much as a specific algorithm, but as a tool which is orthogonal to a lot of the major planning techniques out there. Thus, in principle one could apply E-graphs to any of the state-of-the-art A* heuristic-based planners, and one might even adapt the method to get anytime, incremental search using experiences in symbolic domains.

Finally, E-Graphs could potentially find other uses, in particular for replanning. If an unexpected event invalidates a robot's plan mid-execution, the replanner can remember the original solution as an E-graph to encourage reparations along the old path. In addition to speeding replanning, the E-graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan. Minimizing disruption is important when resources must be allocated according to the plan, or cognitively-burdened humans are involved with its execution.

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
% AAAI format packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
% Additional packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{comment}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
% END Additional packages
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Experience-Biased Symbolic Planning)
/Author (Aram Ebtekar, Mike Phillips, Sven Koenig, Maxim Likhachev)
/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Experience-Biased Symbolic Planning}
\author{Aram Ebtekar$^\dagger$ \and Mike Phillips$^\dagger$ \and Sven Koenig\thanks{University of Southern California, Los Angeles, CA 90089} \and Maxim Likhachev% <-this % stops a space
\thanks{Carnegie Mellon University, Pittsburgh, PA 15217}% <-this % stops a space
%
}
\maketitle
\begin{abstract}
\begin{quote}
Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
In this paper, we demonstrate how to augment symbolic planners with
experience graphs, using the HSP2 planner as a representative
example.
The resulting planners are able to trade off seamlessly
between plan quality and runtime and thus have advantages over past
plan-reuse techniques, such as planning by analogy.
We demonstrate experimentally that on many symbolic domains, our approach reduces the number of nodes that the HSP2 planner needs to consider by a factor of 2 or more while achieving about the same plan quality.
\end{quote}
\end{abstract}

\section{Introduction}

\begin{comment}
Planning entails finding action sequences that achieve a goal state.
In order to apply the language of graph theory, states are often thought of as nodes connected by action transitions.
A \textbf{plan} is a path from the start state to one of many goal states.
Despite the existence of classic polynomial-time search techniques, such as Dijkstra's algorithm, planning remains the crux of many difficult problems in AI.

@@

\end{comment}

In forward weighted A* search, a frontier of nodes expands from the start until it hits a goal, at which point a solution is found. \textbf{Heuristics} are cheaply computable approximations of the remaining distance from a goal to the node. A* uses these to focus the search toward the goal.

However, without domain expert knowledge, symbolic planning problems can be very difficult. A state-of-the-art domain-independent planner, or even a human faced with an unfamiliar kind of puzzle, might have great difficulty. Like a human, then, one might hope that a planning agent would similarly learn to generalize solutions from past planning experiences to related new instances.

A recent approach builds \textbf{experience graphs} (E-graphs) to estimate the high-level connectivity of the free space in motion planning tasks \cite{phillips2012graphs}.
The intuition is to remember previously generated paths so that, when a new start and goals are queried, a new path can be quickly generated by reusing subpaths from the E-graph.
A variant of weighted A* is employed which biases its focus toward the E-graph.
While this work demonstrates promising results in robot motion planning, E-graphs have never before been applied to symbolic domain representations such as the STRIPS language.

@@

Classically, case-based reasoning methods 
such as PRIAR~\cite{Kamb:92}, SPA~\cite{Hank:95}, MRL~\cite{Koeh:94}, and NoLimit~\cite{mljournal}
have been used to recall 
previous plans that appear similar to the current problem and 
then adapt them to meet the new specifications.
Compared to these methods, our work reuses prior experience in
the context of modern weighted A* based methods for symbolic planning. We also provide
a bound on the suboptimality of the solution.

@@

OAKplan~\cite{Serina:2010:KFC:1860143.1860472} is a recent 
case-based reasoning method which converts 
planning instances into a compact graph representation and 
then uses recent kernel methods for matching labeled graphs to select
a similar case to the problem at hand. The selected case is then 
adapted using LPG-ADAPT~\cite{Fox06planstability} LPG-ADAPT is a replanning method
that encourages \textit{plan stability}, which tries to make 
sure that the new plan is as similar to the previous plan as possible. 
The method also uses a modern heuristic search approach.

@@

\begin{defn} For $\epsilon\ge 1$, a heuristic $h$ is called \textbf{$\epsilon$-consistent} iff $h(S) = 0$ when $S$ is a goal and $h(S) \le \epsilon c(S,S') + h(S')$ for all $S,S'\in V$. $h$ is \textbf{consistent} if it is $1$-consistent. \end{defn}
\begin{thm} Given an $\epsilon$-consistent heuristic, A* without reexpansions is guaranteed to find a path costing no more than $\epsilon$ times the optimal path cost \cite{LikGorThr-ara}. \end{thm}

@@

% TODO delete
In a sense, a lot of work is wasted by estimating the cost to reach every atom, when we only require $g_S(G)$.
Later, we'll see how to make better use of this computation.

@@

E-graphs can improve total search time over a series of related queries on the same graph.
Formally, an E-graph is a subgraph of the state space.
It is updated between queries, typically by adding the solution path from the previous search query.

Suppose we have a consistent heuristic $h(S,S')$ for the distance between arbitrary pairs of states.
That is, $h$ obeys the triangle inequality, is never dominated by an edge cost, and $h(S,S) = 0$ for all $S\in V$.
%TODO Planning with E-graph is simply running A* or WA* with heuristic h^E.
The E-graph heuristic $h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
To be precise, define

@@

Let $V^E$ be the union of the goal states and the E-graph's vertices.
In addition to following E-graph edges, we imagine it's possible to ``jump" from any $S\in V^E$ to any $S'\in V^E$ at cost $\epsilon^E h(S,S')$.
That is, let $c'(S,S') = \min\left(c^E(S,S'),~\epsilon^E h(S,S')\right)$

@@

Later, when generating $S \notin V^E$, we see that we have already precomputed costs of paths consisting of all but the first edge of the minimizing path $\pi$ in the definition of $h^E(S)$. Thus, we derive the mathematically equivalent but much cheaper computation
\[h^E(S) = \min_{S'\in V^E} \left(\epsilon^E h(S,S') + h^E(S')\right)\]

\begin{thm} If the base heuristic $h$ is consistent, then $h^E$ is $\epsilon^E$-consistent. \cite{phillips2012graphs}\end{thm}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Pentagon.png}
	\end{center}
	\caption{An example E-graph and corresponding $h^E$-values.}
	\label{fig:example}
\end{figure}

@@

We now combine the ideas from HSP2 and E-graphs to construct a domain-independent STRIPS planner which learns from experience. In STRIPS, a consistent heuristic $h(S,S')$ is given by the HSP-max estimate $g_S(S')$. We can compute $g_S(S')$ for all $S,S'\in V^E$ in precisely $|V^E|$ runs of Algorithm \ref{alg:ComputeG}: each run provides us with $|V^E|$ of these results, yielding $(|V^E|)^2$ values in total.

@@

ComputeG($S$) implements the dynamic programming computation of $g_S$-values.
Each iteration of the outermost loop permanently fixes at least one $g_S(a)$ value, so it does at most $|A|+1$ iterations.
Multiplying nested loop iterations together and dropping cardinality signs for brevity, a conservative runtime bound on Algorithm \ref{alg:ComputeG} is $O(\mathbf{A^2O})$.
Therefore, it costs $O(\mathbf{A^2O + V^EA})$ time to generate each state.

@@

\begin{thm}
If there exists a path from initial state $I$ to a goal state $S\supseteq G$, the experience-biased HSP-max search algorithm finds a path which is at most $\epsilon\epsilon^E$-suboptimal.
\end{thm}

@@

%TODO Finally, we remark that the Experience-Biased HSP algorithm is highly parallelizable, even if A* is retricted to expanding nodes sequentially. Recall that the sum, min and max functions are computable in logarithmic time using linearly many processors. Therefore, with minor adjustments, ComputeG($S$) has parallel depth $O(\mathbf{A\log A\log O})$. With $\mathbf{A\max(O,V^E)}$ processors, the total cost of generating a state is $O(\mathbf{(A\log O + \log V^E)\log A})$. Using even more processors, the cost of \textit{expanding} a state can be reduced to the same by generating its successors in parallel. If still more processors are available, some may be dedicated to the task of preemptively computing $h^E$ for states that are likely to be generated in the future, e.g. near the A* frontier.

@@

\subsection{Experiment 1: Reusing Fragmented Experiences}

In this experiment set, we solve several hundred problem instances across 18 domains from the test suite.
For each problem, we first plan without experiences, using the HSP-plus heuristic in an A* search with weight $\epsilon=5$.
This search acts as our scientific \textbf{control}.
If the control fails to find a solution within 5 seconds (on an Intel Core i7-2600), we discard the problem instance.
Otherwise, we record the plan cost and the number of states that were generated during the search.
Thus, we end up recording data for 321 problem instances.

For each of these, we run 3 additional searches using E-graphs, setting $\epsilon^E=5$ but reducing $\epsilon$ to 1, thus maintaining the same theoretical suboptimality bound as planning without E-graphs weighted by $\epsilon=5$.
(Note that although $\epsilon = 1$, some inflation is implicit in the use of HSP-plus.
HSP-plus may overestimate by a factor equal to the number of atoms in the goal in the worst case, but only if the atoms are highly coupled together.)

The E-graph consists of 20\%, 50\% or 80\% of the edges selected at random from the control's solution path, over the 3 respective searches. For each of these, we again record the solution cost and number of nodes generated, and compare these figures against the control.
We define \textbf{speedup} as the ratio of the number of nodes generated in the control to the number generated in the E-graph search.
Likewise, we define the \textbf{cost improvement} as the ratio of solution cost in the control to cost in the E-graph search.

Results are summarized in Table \ref{tab:percent}.
To estimate the typical range of speedups, we present the 25th and 75th percentile speedups among the instances of each domain.
The full data is plotted in Figures \ref{fig:s_20_0} to \ref{fig:s_80_0}.
We see that, while performance is virtually unaffected in some domains, it's never substantially worsened, and in certain domains the experience helps greatly.
For example, results are highly encouraging in the Blocks domain.
Furthermore, Figure \ref{fig:c_50_0} shows that the solution quality remains competitive; indeed, we see that when E-graphs are employed, the path cost is slightly reduced on average.

@@

\subsection{Experiment 2: Reusing Nearby Experiences}

The previous experimental setup tested our ability to complete partial plans that are fragmented by gaps; however, the experimental searches solved identically the same problems as the control used to generate the E-graph.
Now, we try changing the start and goal states by moving each of them a small distance within the state space. 
In this manner, we test how well E-graphs enable the planner to generalize to nearby but non-identical queries.

We narrow our focus to 13 domains, and take from each of them the same set of instances as in Experiment 1, yielding 218 problem instances in all.
This time, we save 100\% of the solution path found by the same control used in Experiment 1.
Then, for each problem, we form 3 modified problems where the start and goal are each displaced by 5, 20 or 50 steps of random walk along the graph, respectively.
Note that, due to the unpredictable nature of random walks, the shortest-paths distances of the moved nodes from their initial positions is only bounded from above by the number of steps taken, and may vary widely.

@@

%TODO trend speedup vs nodesgen
Figures \ref{fig:s_20_0} to \ref{fig:s_100_50} display the individual speedups achieved over all of our experimental trials. We observe that cases in which E-graphs mislead the planner into generating more states are quite rare, so it seems experiences can only help. We set the bias parameters arbitrarily; tuning them by domain or problem size may well yield even better results.

@@

However, some additional work remains before state-of-the-art performance can be achieved.
Aside from engineering optimizations and integration with newer state-of-the-art heuristics, future work will need to consider more intelligent ways to generalize from the experiences encoded by E-graphs.
This presents a unique challenge in symbolic planning, as many distinct states which may even be a large distance apart in the state graph, may still be conceptually related.
Thus, a planner could potentially benefit by learning to transfer experiences between parts of the state space which are somehow related.
With such an approach, it would be essential to limit overgeneralization, so as not to waste time on a lot of false leads.

@@

We saw that, by reusing pieces from past plans, E-graph-based planners can find solutions more quickly as they learn and acquire experiences. Many interesting directions remain for future investigation. It remains unclear how the bias parameters should be set. In addition, more advanced schemes will be needed to expand and prune E-graphs if they get large due to collecting a lot of solutions. Saving each computed plan seems like a good idea intuitively, but other possibilities may be worth investigating.

For STRIPS in particular, distinct states can actually be very similar, differing only by a few irrelevant atoms; hence, experiences should be transferable to inexact matches. However, it's crucial not to overgeneralize as that might simply lead to most of the graph being reweighted uniformly. The problem of generalization seems related to that of abstraction, or automatically extracting structural information from a symbolic domain or problem description.

E-Graphs should be thought of not so much as a specific algorithm, but as a tool which is orthogonal to a lot of the major planning techniques out there. Thus, in principle one could apply E-graphs to any of the state-of-the-art A* heuristic-based planners, and one might even adapt the method to obtain anytime, incremental search for using experiences in symbolic domains.

Finally, E-Graphs could potentially find other uses, in particular for replanning. If an unexpected event invalidates a robot's plan mid-execution, the replanner can remember the original solution as an E-graph to encourage reparations along the old path. In addition to speeding up replanning, the E-graph could result in a less disruptive solution, in the sense that it avoids unnecessarily deviating from the original plan. Minimizing disruption is important when resources must be allocated according to the plan, or cognitively-burdened humans are involved with its execution.
